Learning to Pivot with Adversarial Networks

### 2017-05-18 tex/nips/nips_2017.tex
new abstract

\begin{abstract}
    % Many inference problems involve data generation processes that are not uniquely
    % specified or are uncertain in some way.
    In a scientific context, the presence of
    several plausible data generation processes is often associated to systematic uncertainties. Robust inference is possible if it is based on a
    pivot -- a quantity whose distribution does not depend on the unknown value of the
    (typically continuous) nuisance parameters that parametrize this family of
    generation processes. In this work,  we introduce a training procedure
    based on adversarial networks for enforcing the pivotal property on a predictive model.
    We derive theoretical results showing that the procedure tends
    towards a minimax solution corresponding to a predictive model that is both
    optimal and independent of the nuisance parameters (if that model exists) or
    for which one can tune a trade-off between accuracy and robustness. We
    demonstrate the effectiveness of this approach with a toy example and an example
    from particle physics.
\end{abstract}

>>>>

\begin{abstract}
Several techniques for domain adaptation have been proposed to account for differences in the
distribution of the data used for training and testing. The majority of this work focuses on
a binary domain label. Similar problems occur in a scientific context where there may be a continuous family of
plausible data generation processes associated to the presence of systematic uncertainties. 
Robust inference is possible if it is based on a
    pivot -- a quantity whose distribution does not depend on the unknown value of the
    nuisance parameters that parametrize this family of
    data generation processes. In this work,  we introduce and derive theoretical results
     for ta training procedure
    based on adversarial networks for enforcing the pivotal property (or, equivalently, fairness with respect to continuous attributes) on a predictive model.
    The method includes a hyperparameter, which one can tune a trade-off between accuracy and robustness. We
    demonstrate the effectiveness of this approach with a toy example and an examples
    from particle physics.
\end{abstract}

%\begin{abstract}
%    % Many inference problems involve data generation processes that are not uniquely
%    % specified or are uncertain in some way.
%    In a scientific context, the presence of
%    several plausible data generation processes is often associated to systematic uncertainties. Robust inference is possible if it is based on a
%    pivot -- a quantity whose distribution does not depend on the unknown value of the
%    (typically continuous) nuisance parameters that parametrize this family of
%    generation processes. In this work,  we introduce a training procedure
%    based on adversarial networks for enforcing the pivotal property on a predictive model.
%    We derive theoretical results showing that the procedure tends
%    towards a minimax solution corresponding to a predictive model that is both
%    optimal and independent of the nuisance parameters (if that model exists) or
%    for which one can tune a trade-off between accuracy and robustness. We
%    demonstrate the effectiveness of this approach with a toy example and an example
%    from particle physics.
%\end{abstract}
